Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-22 ms.tex
still writing introduction

Both SFD/FDS99 DIRBE temperature limitation.
Planck allows us to get around temperature limitation. One sentence overview of
Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.

>>>>

Both SFD/FDS99 dust temperature maps are limited to $1.3^{\circ}$ resolution 
due to their reliance on DIRBE to constrain the dust SED shape. \PLANCK's 
combination of excellent sensitivity and resolution on the Rayleigh-Jeans
side of the dust spectrum's peak allow for the construction of a full-sky dust 
temperature with near-\IRAS~angular resolution. Multiple \PLANCK-based full-sky
thermal dust model are presently available. \cite{planckdust} modeled the
\PLANCK~based dust SED from 353-3000 GHz using a single MBB model in which
beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
\cite{meisner15} applied the FDS99 two-component emission
